### 2023-04-28 cv/cv-body.tex
Add missing paper
Update cv

\begin{description}
\tightlist
\item[2022]
Lindmark, M., \textbf{S.C. Anderson}, M. Gogina, M. Casini. Evaluating
drivers of spatiotemporal individual condition of a bottom-associated
marine fish. bioRxiv 2022.04.19.488709.
\url{https://doi.org/10.1101/2022.04.19.488709}.
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett.
sdmTMB: an R package for fast, flexible, and user-friendly generalized
linear mixed effects models with spatial and spatiotemporal random
fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

@@

\url{https://doi.org/10.1016/j.pocean.2020.102393}

@@

\begin{description}
\tightlist
\item[2022]
Grandin, C.J., \textbf{S.C. Anderson}, P.A. English. Arrowtooth Flounder
(\emph{Atheresthes stomias}) Stock Assessment for the West Coast of
British Columbia in 2021. Accepted DFO Can. Sci. Advis. Sec. Res. Doc.
\item[2022]
DFO. A data synopsis for British Columbia groundfish: 2021 data update.
DFO Can. Sci. Advis. Sec. Sci. Resp. 2022/020.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-fra.html}{French
version}).
\item[2021]
DFO. Status Update of Pacifc Cod (\emph{Gadus macrocephalus}) for West
Coast Vancouver Island (Area 3CD), and Hecate Strait and Queen Charlotte
Sound (Area 5ABCD) in 2020. DFO Can. Sci. Advis. Sec. Sci. Resp.
2021/002.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-fra.html}{French
version}).
\item[2021]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia. DFO
Can. Sci. Advis. Sec. Res. Doc. 2021/007.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{Research
Document},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}).
\item[2021]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockfish (\emph{Sebastes ruberrimus}) in British
Columbia. DFO Can. Sci. Advis. Sec. Res. Doc. 2021/008.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_008-eng.html}{Research
Document}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

\hypertarget{government-technical-reports}{%
\section{Government Technical
Reports}\label{government-technical-reports}}

\begin{description}
\tightlist
\item[2021]
English, P.A., \textbf{Anderson, S.C.}, and Workman, G.D. A review of
groundfish surveys in 2019. In State of the physical, biological and
selected fishery resources of Pacific Canadian Marine Ecosystems in
2019. Edited by J.L. Boldt, A. Javorski, and P.C. Chandler.
pp.\ 127--133. Can. Tech. Rep.\ Fish. Aquat. Sci. 3434, Sidney, BC.
(\href{https://publications.gc.ca/site/eng/9.900827/publication.html}{English
version}).
\item[2020]
English, P.A., \textbf{Anderson, S.C.}, and Workman, G.D. A review of
groundfish surveys in 2019. In State of the physical, biological and
selected fishery resources of Pacific Canadian Marine Ecosystems in
2019. Edited by J.L. Boldt, A. Javorski, and P.C. Chandler.
pp.\ 102--106. Can. Tech. Rep.\ Fish. Aquat. Sci. 3377, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2019/index-eng.html}{English
version}).
\item[2019]
\textbf{Anderson, S.C.}, and Workman, G.D. A review of groundfish
surveys in 2018 and an introduction to the groundfish data synopsis
report. In State of the physical, biological and selected fishery
resources of Pacific Canadian marine ecosystems in 2018. Edited by J.L.
Boldt, J. Leonard, and P.C. Chandler. pp. 90--94. Can. Tech. Rep.\ Fish.
Aquat. Sci. 3314, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2018/index-eng.html}{English
version}).
\item[2018]
Edwards, A.M., Duplisea, D.E., Grinnell, M.H., \textbf{Anderson, S.C.},
Grandin, C.J., Ricard, D., Keppel, E.A., Anderson, E.D., Baker, K.D.,
Benoit, H.P., Cleary, J.S., Connors, B.M., Desgagnes, M., English, P.A.,
Fishman, D.F., Freshwater, C., Hedges, K.J., Holt, C.A., Holt, K.R.,
Kronlund, R., Mariscak, A., Obradovich, S.G., Patten, B.A., Rogers, B.,
Rooper, C.N., Simpson, M.R., Surette, T.J., Tallman, R.F., Wheeland,
L.J., Wor, C., and Zhu, X. 2018. Proceedings of the Technical Expertise
in Stock Assessment (TESA) national workshop on ``Tools for transparent,
traceable, and transferable assessments'' 27--30 November 2018 in
Nanaimo, British Columbia. Can. Tech. Rep.\ Fish. Aquat. Sci. 3290,
Nanaimo, BC.
(\href{https://waves-vagues.dfo-mpo.gc.ca/Library/40750152.pdf}{English
version}).
\end{description}

@@

\begin{description}
\tightlist
\item[2020--21]
Co-principal Investigator on NOAA Office of Science and Technology
NMFS-DFO grant ``Characterizing range shifts in groundfish species in
response to local climate velocities''. An extension to apply methods
from a similarly titled ACCASP grant below to NOAA waters.
\item[2020--21]
Collaborator on NOAA Office of Science and Technology NMFS-DFO grant
``Groundfish distribution shifts between British Columbia, Canada, and
Southeast Alaska, USA: climate drivers, ecosystem impacts and management
implications''.
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{http://www.nrcresearchpress.com/page/cjfas/award} A
``lectureship conferred upon a young, energetic and creative researcher
at the cutting edge of an aquatic discipline''.
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

>>>>

\begin{description}
\tightlist
\item[2023]
Liu, O.R. E.J. Ward, \textbf{S.C. Anderson}, K.S. Andrews, L.A.K.
Barnett, S. Brodie, G. Carroll, J. Fiechter, M.A.\ Haltuch, C.J. Harvey,
E.L. Hazen, P.Y. Hernvann, M. Jacox, I.C. Kaplan, S. Matson, K. Norman,
M.P. Buil, R.L. Selden, A.O. Shelton, J.F. Samhouri. Species
redistribution creates unequal outcomes for multispecies fisheries under
projected climate change.
\url{https://doi.org/10.21203/rs.3.rs-2399110/v1}.
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett.
sdmTMB: an R package for fast, flexible, and user-friendly generalized
linear mixed effects models with spatial and spatiotemporal random
fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2022]
Lindmark, M., \textbf{S.C. Anderson}, M. Gogina, M. Casini. Evaluating
drivers of spatiotemporal individual condition of a bottom-associated
marine fish. bioRxiv 2022.04.19.488709.
\url{https://doi.org/10.1101/2022.04.19.488709}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

\item[2023]
Free, C.M., \textbf{S.C. Anderson}, E.A. Hellmers, B.A. Muhling, M.O.
Navarro, K. Richerson, L.A. Rogers, W.H. Satterthwaite, A.R. Thompson,
J.M. Burt, S.D. Gaines, K.N. Marshall, J.W. White, and L.F. Bellquist.
Impact of the 2014--2016 marine heatwave on US and Canada West Coast
fisheries: Surprises and lessons from key case studies. Fish and
Fisheries. In press. \url{https://doi.org/10.1111/faf.12753}.
\item[2023]
Thompson, P.L., \textbf{S.C. Anderson}, J. Nephin, C.K. Robb, B.
Proudfoot, A.E. Park, D.R. Haggarty, E.M. Rubidge. Integrating trawl and
longline surveys across British Columbia improves groundfish
distribution predictions. Can. J. Fish. Aquat. Sci. 80(1): 195--210.
\url{https://doi.org/10.1139/cjfas-2022-0108}.

@@

\url{https://doi.org/10.1016/j.pocean.2020.102393}.

@@

\begin{description}
\tightlist
\item[2023]
Barrett, T.J., J.R. Marentette, R.E. Forrest, S.C. Anderson, C.A. Holt,
D.W. Ings, M.E. Thiess. Technical Considerations for Stock Status and
Limit Reference Points under the Fish Stocks Provisions. Accepted DFO
Can. Sci. Advis. Sec. Res. Doc.
\item[2022]
Grandin, C.J., \textbf{S.C. Anderson}, P.A. English. Arrowtooth Flounder
(\emph{Atheresthes stomias}) Stock Assessment for the West Coast of
British Columbia in 2021. Accepted DFO Can. Sci. Advis. Sec. Res. Doc.
\item[2022]
DFO. A data synopsis for British Columbia groundfish: 2021 data update.
DFO Can. Sci. Advis. Sec. Sci. Resp. 2022/020.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-fra.html}{French
version}).
\item[2021]
DFO. Status Update of Pacifc Cod (\emph{Gadus macrocephalus}) for West
Coast Vancouver Island (Area 3CD), and Hecate Strait and Queen Charlotte
Sound (Area 5ABCD) in 2020. DFO Can. Sci. Advis. Sec. Sci. Resp.
2021/002.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-fra.html}{French
version}).
\item[2021]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia. DFO
Can. Sci. Advis. Sec. Res. Doc. 2021/007.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{Research
Document},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}).
\item[2021]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockfish (\emph{Sebastes ruberrimus}) in British
Columbia. DFO Can. Sci. Advis. Sec. Res. Doc. 2021/008.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_008-eng.html}{Research
Document}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

\hypertarget{technical-reports}{%
\section{Technical Reports}\label{technical-reports}}

\begin{description}
\tightlist
\item[2023]
ICES. Workshop on Unavoidable Survey Effort Reduction 2 (WKUSER2). ICES
Scientific Report, 5(13).
\url{https://doi.org/10.17895/ices.pub.22086845.v1}. Co-lead author of
chapter ``TOR III. Modeling and simulations: Further develop model
performance evaluation through simulations, use of auxiliary information
to improve survey data products, including appropriate propagation of
uncertainty''
\item[2021]
English, P.A., \textbf{Anderson, S.C.}, and Workman, G.D. A review of
groundfish surveys in 2019. In State of the physical, biological and
selected fishery resources of Pacific Canadian Marine Ecosystems in
2019. Edited by J.L. Boldt, A. Javorski, and P.C. Chandler.
pp.\ 127--133. Can. Tech. Rep.\ Fish. Aquat. Sci. 3434, Sidney, BC.
(\href{https://publications.gc.ca/site/eng/9.900827/publication.html}{English
version}).
\item[2020]
English, P.A., \textbf{Anderson, S.C.}, and Workman, G.D. A review of
groundfish surveys in 2019. In State of the physical, biological and
selected fishery resources of Pacific Canadian Marine Ecosystems in
2019. Edited by J.L. Boldt, A. Javorski, and P.C. Chandler.
pp.\ 102--106. Can. Tech. Rep.\ Fish. Aquat. Sci. 3377, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2019/index-eng.html}{English
version}).
\item[2019]
\textbf{Anderson, S.C.}, and Workman, G.D. A review of groundfish
surveys in 2018 and an introduction to the groundfish data synopsis
report. In State of the physical, biological and selected fishery
resources of Pacific Canadian marine ecosystems in 2018. Edited by J.L.
Boldt, J. Leonard, and P.C. Chandler. pp. 90--94. Can. Tech. Rep.\ Fish.
Aquat. Sci. 3314, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2018/index-eng.html}{English
version}).
\item[2018]
Edwards, A.M., Duplisea, D.E., Grinnell, M.H., \textbf{Anderson, S.C.},
Grandin, C.J., Ricard, D., Keppel, E.A., Anderson, E.D., Baker, K.D.,
Benoit, H.P., Cleary, J.S., Connors, B.M., Desgagnes, M., English, P.A.,
Fishman, D.F., Freshwater, C., Hedges, K.J., Holt, C.A., Holt, K.R.,
Kronlund, R., Mariscak, A., Obradovich, S.G., Patten, B.A., Rogers, B.,
Rooper, C.N., Simpson, M.R., Surette, T.J., Tallman, R.F., Wheeland,
L.J., Wor, C., and Zhu, X. 2018. Proceedings of the Technical Expertise
in Stock Assessment (TESA) national workshop on ``Tools for transparent,
traceable, and transferable assessments'' 27--30 November 2018 in
Nanaimo, British Columbia. Can. Tech. Rep.\ Fish. Aquat. Sci. 3290,
Nanaimo, BC.
(\href{https://waves-vagues.dfo-mpo.gc.ca/Library/40750152.pdf}{English
version}).
\end{description}

@@

\begin{description}
\tightlist
\item[2020--21]
Co-principal Investigator on NOAA Office of Science and Technology
NMFS-DFO grant ``Characterizing range shifts in groundfish species in
response to local climate velocities''. An extension to apply methods
from a similarly titled ACCASP grant below to NOAA waters.
\item[2020--21]
Collaborator on NOAA Office of Science and Technology NMFS-DFO grant
``Groundfish distribution shifts between British Columbia, Canada, and
Southeast Alaska, USA: climate drivers, ecosystem impacts and management
implications''.
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{https://cdnsciencepub.com/journal/cjfas/about} A
``lectureship conferred upon a young, energetic and creative researcher
at the cutting edge of an aquatic discipline''.
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}
